TreehopperFitness: Run this file for all stats, tables, and figures

### 2023-08-23 manuscript/Manuscript_runfile.Rmd
Consolidated construction of `strats_data` for `Publilia-02-strats.Rmd` and moved that code to `Publilia-02-qc.Rmd`. Resolves https://github.com/micahpf/PubliliaFitness/issues/3#issuecomment-1676152818

@@

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))

strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
```

@@

*First, we build logical columns for each of the desired filters for different text sections and figures. This way we can keep the total universe of data in one place and ensure that we are certain which data are being left out and why.*
```{r}
strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)

strats_data_with_filters <- strats_data %>%
  # Add whether female was visited within first 4 days of initiating
  group_by(location) %>%
    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
  ungroup() %>%
  # Add some additional metrics for human readability
  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
                                      "Visited", "Not visited"),
         ants = ifelse(ants_removed, "Ants removed", "Control"),
         est_hatch = as_date(ifelse(is.na(hatch_date),
                                 initiation_date + 20,
                                 hatch_date)),
         est_rel2h = visit_ends-est_hatch) %>%
  # Add day of first visit bins
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
                                              "5+","never visited"))) %>%
  # Remove one female who has dubious data (See note ** below)
  #filter(!is.na(vis_cat)) %>%
  # Build logicals representing inclusion in different plots
  mutate(`Text: 4 different strats` =
           !females_removed & 
           clutch_visited_order == 1 &
           !is.na(num_at_init),
         `Figure 4 (dur vs 1st visit)` = 
           !females_removed & 
           mom_at_init &
           clutch_initiated_order == 1 & 
           !grepl("U", Female_ID) & 
           visit_ends < last_day_fID &
           !is.na(num_at_init),
         `Figure 3 (dur histograms)` = 
           !females_removed & 
           mom_at_init &
           clutch_initiated_order == 1 &
           !grepl("U", Female_ID) & 
           visit_ends < last_day_fID & 
           !is.na(`visited in 4 days`) &
           !is.na(num_at_init))

@@

Visits by secondary females were typically short (median = X days) and only 2 visitors remained through hatching (Figure 2B). 
```{r}
visited_1st_4d_data_tb %>%
  filter(!females_removed,
         !mom_at_init,
         visit_ends < last_day_fID) %>%
  summarize(n = n(),
            n_NA = sum(is.na(guard_duration)),
            mean_gd = mean(as.numeric(guard_duration, "days"), na.rm=T),
            med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))
```

>>>>

```{=html}
<style type="text/css">
  .book .book-body .page-inner {
    max-width: 1600px;
    margin-left: auto;
    margin-right: auto;
  }
details > summary {
  display: list-item;
}
</style>
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 6)

library(kableExtra)   ## Needed if rendering tables
```

@@

```{r}
library(here)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)

theme_set(theme_bw())
```

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
strats_data <- read_rds(here("saved_rds/strats_data.rds"))
```

@@

*First, we build logical columns for each of the desired filters for different text sections and figures. This way we can keep the total universe of data in one place and ensure that we are certain which data are being left out and why.*
```{r}
strats_data_with_filters <- strats_data %>%
  # Remove one female who has dubious data (See note ** below)
  #filter(!is.na(vis_cat)) %>%
  # Build logicals representing inclusion in different plots
  mutate(`Text: 4 different strats` =
           !females_removed & 
           clutch_visited_order == 1 &
           !is.na(num_at_init),
         `Figure 4 (dur vs 1st visit)` = 
           !females_removed & 
           mom_at_init &
           clutch_initiated_order == 1 & 
           !grepl("U", Female_ID) & 
           visit_ends < last_day_fID &
           !is.na(num_at_init),
         `Figure 3 (dur histograms)` = 
           !females_removed & 
           mom_at_init &
           clutch_initiated_order == 1 &
           !grepl("U", Female_ID) & 
           visit_ends < last_day_fID & 
           !is.na(`visited in 4 days`) &
           !is.na(num_at_init))

@@

Visits by secondary females were typically short (median = X days) and only 2 visitors remained through hatching (Figure 2B). 
```{r}
strats_data_with_filters %>%
  filter(!females_removed,
         !mom_at_init,
         visit_ends < last_day_fID) %>%
  summarize(n = n(),
            n_NA = sum(is.na(guard_duration)),
            mean_gd = mean(as.numeric(guard_duration, "days"), na.rm=T),
            med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))

# visited_1st_4d_data_tb %>%
#   filter(!females_removed,
#          !mom_at_init,
#          visit_ends < last_day_fID) %>%
#   summarize(n = n(),
#             n_NA = sum(is.na(guard_duration)),
#             mean_gd = mean(as.numeric(guard_duration, "days"), na.rm=T),
#             med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))
```
